Handling String-Number Conversion in String Constraint Solving

### 2019-11-19 draft.tex
fix typos

@@

Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed. \cite{????}).
The path feasibility problem is usually solved by a reduction to the satisfiability of a formula. More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)}  solvers. The types of constraints needed depend on the types of program expressions to be analyzed; therefore, SMT solvers must support different combinations of theories to handle a wide range of types.

In particular, \emph{string data}  is omnipresent in modern programming languages, especially in Web code that gets input as strings.  Various infamous security vulnerabilities, such as injection and cross-site scripting attack, can be caused by malicious string values.  Therefore, solving string constraint has received considerable attention in the constraint solving community.
Among all types of program variables, \emph{string data type}  is omnipresent in modern programming languages.  Various  security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.  Therefore, string constraint solving has received considerable attention in the constraint solving community. 
Operations such as \emph{equality constraints} (e.g. $x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4  \cite{?}, OSTRICH \cite{}, Sloth \cite{},   Trau+ \cite{?},  Z3  \cite{?} and Z3Str3  \cite{?}. 
  However,   solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.  When there is support, it is often very limited. Thus, $n = \sti{\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
are core operations that require stronger solver support to handle real code.

@@

More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$. After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints. For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA. We do not set any restriction to the selection of PFA for other string variables. The selection is an implementation decision. We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.

>>>>

\yfc{We need an abstract}

@@

Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed. \cite{????}.
The path feasibility problem is usually solved by a reduction to the satisfiability of a formula. More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)} solvers. The types of constraints needed depend on the types of program expressions to be analyzed; therefore, SMT solvers must support different combinations of theories to handle a wide range of types.

Among all types of program variables, \emph{string data type} is omnipresent in modern programming languages. Various security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values. Therefore, string constraint solving has received considerable attention in the constraint solving community. 
Operations such as \emph{equality constraints} (e.g. $x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{?}, Z3 \cite{?} and Z3Str3 \cite{?}. 
However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form. When there is support, it is often very limited. Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations that require stronger solver support to handle real code.

@@

More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$. After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints. For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA. We do not set any restriction to the selection of PFA for other string variables. The selection is an implementation decision. We will describe the PFA selection strategy of {\tool} in Section~\ref{section:implementation}.
